Effects of rotation on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-04-29 paper/Analisis.tex
small changes

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifODHOM.png}
    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifOD.png}
    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifSpeedsHOM.png}
    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifSpeeds.png}
\caption{Width of the lyman-alpha line for all the models. 
  \label{figure:widthvstheta}
}
\end{figure*}

@@

To quantify the line broadening we measure a modified version of the full
width at half maximum (FWHM) for half of the line, $W_{1/2}$. It means that in
the case of double peaked emission, $W_{1/2}$ corresponds to the with
one of thepeaks, while in the extreme case when the line is converted
into a single peak, $W_{1/2}$ corresponds to half of the full width.

@@

In Figure \ref{figure:efvsv} we found that in the central distribution the escape fraction does not change with velocity while it
does in the optical depth. On the other hand for the homogeneous distribution
we found that for higher velocities photons escape easily. The
difference between this two results relly in the fact that in the
homogeneous distribution photons are emitted closer to the escape
surface and this makes this configuration more sensitive to
rotation while in the central configuration the escape fraction depends mainly in the amount of gas rather than in rotation.

>>>>

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{WidthvsThetaCentral.png}
    \includegraphics[width=0.45\textwidth]{WidthvsTheta.png}
    \caption{Width of the lyman-alpha line for all the models. 
  \label{figure:widthvstheta}
}
\end{figure*}

@@

To quantify the line broadening we measure a modified version of the full
width at half maximum (FWHM) for half of the line, $W_{1/2}$. It means that in
the case of double peaked emission, $W_{1/2}$ corresponds to the with
one of the peaks, while in the extreme case when the line is converted
into a single peak, $W_{1/2}$ corresponds to half of the full width.

@@

In Figure \ref{figure:efvsv} we found that in the central distribution the escape fraction does not change with velocity while it
does in the optical depth. On the other hand for the homogeneous distribution
we found that for higher velocities photons escape easily. The
difference between this two results relly in the fact that in the
homogeneous distribution photons are emitted closer to the escape
surface and this makes this configuration more sensitive to
rotation while in the central configuration the escape fraction depends mainly in the amount of gas rather than in rotation. \\

Of great importance is to notest that for the homogeneous distribution the optical depth of $\tau_{H}=10^5$ does not follow the trend known for the others. In order to study this FIG.(CLARA plot) \\
